### 2012-08-10 inst/examples/policycosts/L1.Rmd
policycosts compared in L1

``` {r policycost}
costs <- dt[, sum(policy_cost * (1 - delta)^(time - 1)), by = reps]$V1
profits <- dt[, sum(profit_fishing * (1 - delta)^(time - 1)), by = reps]$V1
costs_alt <- dt[, sum(policy_cost_alt * (1 - delta)^(time - 1)), by = reps]$V1
profits_alt <- dt[, sum(profit_fishing_alt * (1 - delta)^(time - 1)), by = reps]$V1

qplot(costs)
qplot(profits)
qplot(profits-costs)
````

>>>>

``` {r policycost}
costs <- dt[, sum(policy_cost * (1 - delta)^(time - 1)), by = reps]$V1
profits <- dt[, sum(profit_fishing * (1 - delta)^(time - 1)), by = reps]$V1
costs_alt <- dt[, sum(policy_cost_alt * (1 - delta)^(time - 1)), by = reps]$V1
profits_alt <- dt[, sum(profit_fishing_alt * (1 - delta)^(time - 1)), by = reps]$V1
````
